Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-02-28 rebuttal/rebuttal_response_max_500_words.txt

We thank the reviewers for their comments. We summarize and respond to them in what follows.

## Metrics and evaluation protocol

> [Reviewer 1] ICDAR Contest in 2011 related to that topic

Thanks for pointing this out. They are essentially using a full-cross evaluation of all methods to perform end-to-end
evaluation, just like us. Also, they do not report NER evaluation, unlike us. We updated the paper with these
clarifications.

> [Reviewer 1] Qualitative analysis of influence of OCR quality on NER

Effects of the OCR noise are indeed non-uniform on NER results. The impact on structuring elements of the entries like
punctuation symbols appears to be most significant, as they mark the separation between semantically homogeneous blocks
(e.g. between PERS and ACT). We plan to carry out a more in-depth qualitative study in the near future.

> [Reviewer 1] The authors take great care to have a clean and reproducible way of projecting expected outcomes onto
> noisy OCR results. The question arises to how useful this is and whether it is not introducing biases in various ways,
> overestimating or underestimating the effects of the NER labeling

The metrics used are the ones commonly used in previous works. Projecting the ground-truth labels on a noisy text was a
sensible way to assess whether NERs could help to correct OCR errors. Here OCR is either pretty good or very wrong, so
alignments usually make sense or can be detected as degenerated cases. However, it is very true that some borderline
cases may cause trouble. This requires more study, and we updated the paper to be more explicit about these limitations.

> [Reviewer 2] Comparing two runs of PERO OCR together, or two runs of Tesseract together

Very good point, but we could not compete with the large, private training datasets used to produce the models we used.
We chose to report, as objectively as possible, the performance of actual, off-the-shelf systems.

> [Reviewer 2] Reason for not reporting Kraken's performance on downstream NER

We chose not to report Kraken's performance as it would have drastically reduced the size of the labelled sets "NER-x" and
thus hampered the other evaluations on the reference, PERO and tesseract datasets. All labelled datasets contain the
same subset of directories entries by construction (section 3). Kraken performs quite poorly, which hinders the
projection of labels from the ground truth and drastically reduces the size of the subset of labelled entries.

> [Reviewer 2] Experiment with artificial OCR noise in future work

We plan to perform such experiments following e.g. the techniques presented in https://doi.org/10.1007/978-3-030-86331-9_48
As it seems to be quite hard to generate realistic noise, we decided to first focus on real cases with no further assumptions.

## Paper organization

> [Reviewer 3] Section 2.3 should be a separate section about the pipeline

We have tried to extract this content as a new section as suggested. However, this change made the sections unbalanced,
and the explication flow disrupted. Moreover, it breaks the 15-pages limits. As a consequence, the overall organization
of the paper was left unchanged.

## Typos, inconsistencies and lack of clarity

> [Reviewer 1] Figure 1 is never referred to in the text
> [Reviewer 1] When referring to figures, you sometimes write "fig. n", "figure n", and "Figure n"
> [Reviewer 1] You wrote Tesseract twice with a lowercase t

Thanks for pointing these issues, we fixed them.

> [Reviewer 3] What are "thumbnails" in page 7

We refer to "thumbnails" as image crops, they have the same resolution as the original image. We updated the text to
clarify this.

> [Reviewer 3] Description of NER QA is confusing
> [Reviewer 3] Figure 4 needs clarification

We clarified the relevant section and fig.4's caption.

### 2022-02-28 rebuttal/rebuttal_response_max_500_words.txt

We thank the reviewers for their comments. We will do our best to update the final version accordingly.

@@

## Metrics and evaluation protocol

> [Reviewer 1] ICDAR 2011 Contest related to that topic

Thanks for pointing this out. They are essentially using a cross evaluation of all methods to perform end-to-end evaluation, just like us, but do not report NER evaluation, unlike us.

@@

> [Reviewer 1] Qualitative analysis of influence of OCR quality on NER

Effects of the OCR noise are indeed non-uniform on NER results. The impact on structuring elements of the entries like punctuation symbols appears to be most significant, as they mark the separation between semantically homogeneous blocks. This is under further study.

> [Reviewer 1] how useful [projecting expected outcomes onto noisy OCR results] is 
> and whether [this] is not introducing biases in various ways, overestimating or underestimating 
> the effects of the NER labeling

We used standard metrics from previous works. Projecting the ground-truth labels on a noisy text was a sensible way to assess whether NERs could help to correct OCR errors. In our experiments, alignments usually make sense or can be detected as degenerated cases. However, it is very true that some borderline cases may cause trouble. We will be more explicit about these limitations.

@@

> [Reviewer 2] Comparing two runs of PERO OCR together, or two runs of Tesseract together

Very good point, but we could not compete with the large, private training datasets used to produce the models we used. We chose to report, as objectively as possible, the performance of actual, off-the-shelf systems.

> [Reviewer 2] Reason for not reporting Kraken's performance on downstream NER

We chose not to report Kraken's performance as it would have drastically reduced the size of the labelled sets used to compare the performance of NER systems, because poor Kraken's performance hinders the projection of labels from the ground truth and creates degenerated cases which are skipped.

@@

> [Reviewer 2] Experiment with artificial OCR noise in future work

We plan to perform such experiments, but as it is hard to generate realistic noise, we decided to first focus on real cases with no further assumptions.

@@

## Paper organization

> [Reviewer 3] Section 2.3 should be a separate section about the pipeline

We have tried to extract this content as a new section as suggested, but this unbalanced sections, disrupted the explication flow, and breaks the 15-pages limits. As a consequence, the overall organization of the paper was left unchanged.

@@

## Typos, inconsistencies and lack of clarity

> [Reviewer 1] Missing Figure 1 reference
> [Reviewer 1] you sometimes write "fig. n", "figure n", and "Figure n"
> [Reviewer 1] Tesseract spelling

Thanks, we fixed this.

### 2022-03-28 rebuttal/rebuttal_response_max_500_words.txt

* [x] ~~?? mettre 1 phrase en future work ?~~

> [Reviewer 1] how useful [projecting expected outcomes onto noisy OCR results] is 
> and whether [this] is not introducing biases in various ways, overestimating or underestimating 
> the effects of the NER labeling

We used standard metrics from previous works. Projecting the ground-truth labels on a noisy text was a sensible way to assess whether NERs could help to correct OCR errors. In our experiments, alignments usually make sense or can be detected as degenerated cases. However, it is very true that some borderline cases may cause trouble. We will be more explicit about these limitations.

* [ ] BD détailler un peu les limitations, être plus explicites à ce sujet

@@

> [Reviewer 2] Comparing two runs of PERO OCR together, or two runs of Tesseract together

Very good point, but we could not compete with the large, private training datasets used to produce the models we used. We chose to report, as objectively as possible, the performance of actual, off-the-shelf systems.

* [ ] EC ajouter une phrase ?? (dire qu'on n'avait même pas assez de données pour faire du fine-tuning)

@@

* [ ] EC

> [Reviewer 3] Description of NER QA is confusing
> [Reviewer 3] Figure 4 needs clarification

We clarified the relevant section and fig.4's caption.

* [ ] EC

## AUTRES

* [ ] NA passe de relecture
* [ ] NA relecture readme dataset + critique structure
* [ ] JC rajouter lien Zenodo dataset
* [ ] ?? dépôt HAL + ArXiV

### 2022-03-28 rebuttal/rebuttal_response_max_500_words.txt

* [x] ~~?? mettre 1 phrase en future work ?~~

> [Reviewer 1] how useful [projecting expected outcomes onto noisy OCR results] is 
> and whether [this] is not introducing biases in various ways, overestimating or underestimating 
> the effects of the NER labeling

We used standard metrics from previous works. Projecting the ground-truth labels on a noisy text was a sensible way to assess whether NERs could help to correct OCR errors. In our experiments, alignments usually make sense or can be detected as degenerated cases. However, it is very true that some borderline cases may cause trouble. We will be more explicit about these limitations.

* [X] BD détailler un peu les limitations, être plus explicites à ce sujet

### 2022-03-28 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
rebuttal points 2/4/5

\subsection{Training and evaluation protocol}
Only CmBERT and CmBERT+ptrn are considered since the first experiment shows that SpaCy NER is outperformed by these two models for all sizes of training sets.
We leverage the labelled sets of entries NER-\emph{reference}, NER-\emph{pero} and NER-\emph{tesseract} created as explained in \cref{sec:dataset}.
Each dataset is split into training development, and test sets following the same protocol as described in \cref{sec:ner-xp1-protocol}, except this time we do not need to create smaller training sets.
As the NER sets contain $8,341$ entries (see \cref{sec:dataset-for-eval}), the produced train sets (resp. development and test) count $6,004$ entries - 72\% of the total (resp. 668 - 8\% and $1,669$ - 20\%).
CmBERT and CmBERT+ptrn are fine-tuned on the training sets built from NER-\emph{reference} and NER-\emph{pero}.
The training parameters are mostly the same as in \cref{sec:ner-xp1-protocol}, only this time the patience threshold is set to 5 evaluations.
Finally the metrics are measured against the three tests sets.

@@

\subsection{Results and discussion}
The measured F1-score are given in \cref{fig:exp_2_eval_ner}.
Results clearly show that models perform best when both the pre-training and the NER fine-tuning share the same characteristics (here, OCR noise) as the texts to be processed.

>>>>

\subsection{Training and evaluation protocol}
Only CmBERT and CmBERT+ptrn are considered since the first experiment shows that SpaCy NER is outperformed for all sizes of training sets.
We leave Kraken aside as its performance hinders the projection of NER labels from the ground truth, thus dramatically reducing the size of labelled sets.
Because the NER metrics are entity-wise, they may underestimate the NER performances on stronly noised texts with fragmented entities.
We leverage the labelled sets of entries NER-\emph{reference}, NER-\emph{pero} and NER-\emph{tesseract} created as explained in \cref{sec:dataset}.
Each dataset is split into training development, and test sets following the same protocol as described in \cref{sec:ner-xp1-protocol}, except this time we do not need to create smaller training sets.
As the NER sets contain $8,341$ entries (see \cref{sec:dataset-for-eval}), the produced train sets (resp. development and test) count $6,004$ entries - 72\% of the total (resp. 668 - 8\% and $1,669$ - 20\%).
CmBERT and CmBERT+ptrn are fine-tuned on the training sets built from NER-\emph{reference} and NER-\emph{pero}.
The training parameters are mostly the same as in \cref{sec:ner-xp1-protocol}, only this time the patience threshold is set to 5 evaluations.
Finally the metrics are measured against the three tests sets.

@@

\subsection{Results and discussion}
The measured F1-score are given in \cref{fig:exp_2_eval_ner}.
Results clearly show that models perform best when both the pre-training and the NER fine-tuning are similar to the processed texts in term of OCR noise.
